An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-26 scagnostics.Rmd
start on section 3

There are a number of properties that a PPI should have, which are:

\textcolor{red}{\cite{posse95b} lists five criteria: minimized by normal distribution, approximately affine invariant, consistent, resistent to features in the tail, fast computation. Comment that different index values for the same plane will make optimisation less efficient. \cite{jones87} moreover lists rotation and translation invariance (independence of choice of basis in the plane), and also mentions conditions for numeric optimisation, i.e. continuous and depending on optimisation methods also differentiable. Interesting: according to \cite{jones87} the original index proposed by Friedman and Tukey did not have property of rotation invariance.}

@@

##Simulation study

@@

###Dataset overview
\label{sec:dataOv}

>>>>

A useful projection pursuit index needs to have several properties. This has been discussed in several seminal papers (\cite{diaconis84}, \cite{huber85}, \cite{jones87}, \cite{posse95b}). The PPI should be  minimized by the normal distribution, because this is not interesting from a data exploration perspective. If all projections are normally distributed, good modeling tools already exist. A PPI should be approximately affine invariant, regardless how the projection is rotated the index value should be the same, and the scale of each variable shouldn't affect the index value. Interestingly the original index proposed by \cite{FT74} was not rotationally invariant. A consistent index means that small perturbations to the sample do not dramatically change the index value. This is particularly important to making optimisation feasible, small angles between projections correspond to small perturbations of the sample, and thus shold be small changes to index value. \cite{posse95b} suggests that indexes should be resistant to features in a tail of the distribution, but this is debatable because one departure from normality that is interesting to detect are anomalous observations. Some PPI are designed precisely for these reasons. Lastly, because we need to compute the PPI over many projections, it needs to be fast to compute. These form the basis of the crteria upon which the scagnostic indexes, and the several alternative indexes are examined:

@@

## Simulation study

@@

### Dataset overview
\label{sec:dataOv}
